\chapter{Introduction}
\section{Context}
\paragraph*{}
Marketing via mobile application has become common in recent times in consumer markets. Either using in app advertisement, or by giving a free trail when using the app.Regarding the increase in smart phone users, and the increased amount of time spend using the hand held device, shows the potential of mobile marketing. On the other hand, it is less common to use smart phones as a marketing channel, when talking about business to business (B2B) products, most often sold via a request for proposals.
\paragraph*{}
IBM shifted from an hardware focused firm to a consulting, software and service company. But this shift is often not recognized at the global market. This turns into a problem, whenever IBM answers a business or software related call for proposal, because the possible customer may not believe, that a - in his or her perception - hardware company has the required skills for his or her problem.
\paragraph*{}
In means of designing a way, to show a potential customer the expertise of IBM, a team focused on migration scenarios in the banking sector, thought of a mobile application or a website as potential marketing instrument. Attempts of designing an application for that matter showed some difficulties, which will be discussed in this paper. It will focus on business to business (B2B) marketing, as well as some psychological and technical issues. Deducing from these topics, generalized requirements will be crafted and afterwards specialized on the given example. 
\section{Problem Statement}